Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-14 paper.tex
Second attempt at query classification

\usepackage{enumerate}
\usepackage{marginnote}
\usepackage[linesnumbered,commentsnumbered,boxed]{algorithm2e}
\usepackage{amsmath}

\newcommand{\acumm}{T-Matrices} % T is for Total!
\newcommand{\ctr}{NewCTR (name subject to change)\ }

@@

The following is a non-comprehensive list of query types that can be efficiently solved with the structures proposed in this work:
\begin{itemize}
    \item \texttt{board\_X$_{LT}$} Number of times that stop X is boarded, optionally restricting to a line L and a time range T.
    \item \texttt{alight\_X$_{LT}$} Number of times that stop X is alighted, optionally restricting to a line L and a time range T.
    \item \texttt{start\_X$_{LT}$} User trips starting at a stop X, optionally restricting to a line L and a time range T.
    \item \texttt{end\_X$_{LT}$} User trips ending at a stop X, optionally restricting to a line L and a time range T.
    \item \texttt{switch\_X$_{LT}$} Number of trips in which the stop X was used to switch lines, optionally restricting to a line L and a time range T.
    \item \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} User trips that originate at stop X to end at stop Y, both being optionally restricted to a line and time range.
    \item \texttt{board\_L$_T$}  Number of times that line L is boarded, optionally restricting to a time range T.
    \item \texttt{alight\_L$_T$} Number of times that line L is alighted, optionally restricting to a time range T.
    \item \texttt{start\_L$_T$} User trips starting at any stop from the line L, optionally restricting to a time range T.
    \item \texttt{end\_L$_T$} User trips ending at any stop from the line L, optionally restricting to a time range T.
    \item \texttt{board\_T} Number of times a user boards within a time range T.
    \item \texttt{alight\_T} Number of times a user alights within a time range T.
    \item \texttt{start\_T} User trips starting within a time range T.
    \item \texttt{end\_T} User trips ending within a time range T.
    \item \texttt{load\_X$_LT$} The average number of passengers traveling from the stop X to its next stop in the line L within the time range T. Can also be seen as the average load of a transport vehicle.

@@

\begin{table}
\caption{Efficiency of \acumm~and \ctr against the queries described in Section~\ref{sec:rq}}
\label{tab:queries}
\begin{tabular}{|l|l|l|}
\hline
Query &  \acumm & \ctr\\
\hline
\texttt{board\_X$_{LT}$} & O(l) & sum of logs \\
\texttt{alight\_X$_{LT}$} & O(l) & Hard$^*$ \\
\texttt{start\_X$_{LT}$} & - & sum of logs \\
\texttt{end\_X$_{LT}$} & - & sum of logs \\
\texttt{switch\_X$_{LT}$} & - & sum of logs \\
\texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} & - & sum of logs \\
\texttt{board\_L$_T$} & O(1) & sum of logs \\
\texttt{alight\_L$_T$} & O(1) & Approx. T \\
\texttt{start\_L$_T$} & - & sum of logs \\
\texttt{end\_L$_T$} & - & O(X) \\
\texttt{board\_T} & O(l) & SuperHard$^*$ \\
\texttt{alight\_T} & O(l) & MegaHard$^*$ \\
\texttt{start\_T} & - & O(l) \\
\texttt{end\_T} & - & SuperHard$^*$ \\
\texttt{load\_X$_LT$} & O(l) & Hard$^*$ \\
\hline
\end{tabular}
\end{table}

@@

>>>>

\usepackage{enumerate}
\usepackage{marginnote}
\usepackage[linesnumbered,commentsnumbered,boxed]{algorithm2e}
\usepackage{amsmath}
\usepackage{threeparttable}

\newcommand{\acumm}{T-Matrices} % T is for Total!
\newcommand{\ctr}{NewCTR (name subject to change)\ }
\newcommand{\ctrq}{NCTRc}

@@

The following is a non-comprehensive list of query types that can be efficiently solved with the structures proposed in this work:
\begin{itemize}
    \item \texttt{board\_X$_{LT}$} Number of times that stop X is boarded, optionally restricting to a line L and a time range T.
    \item \texttt{alight\_X$_{LT}$} Number of times that stop X is alighted, optionally restricting to a line L and a time range T.
    \item \texttt{start\_X$_{LT}$} User trips starting at a stop X, optionally restricting to a line L and a time range T.
    \item \texttt{end\_X$_{LT}$} User trips ending at a stop X, optionally restricting to a line L and a time range T.
    \item \texttt{switch\_X$_{LT}$} Number of trips in which the stop X was used to switch lines, optionally restricting to a line L and a time range T.
    \item \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} User trips that originate at stop X to end at stop Y, both being optionally restricted to a line and time range.
    \item \texttt{board\_L$_T$}  Number of times that line L is boarded, optionally restricting to a time range T.
    \item \texttt{alight\_L$_T$} Number of times that line L is alighted, optionally restricting to a time range T.
    \item \texttt{start\_L$_T$} User trips starting at any stop from the line L, optionally restricting to a time range T.
    \item \texttt{end\_L$_T$} User trips ending at any stop from the line L, optionally restricting to a time range T.
    \item \texttt{board\_T} Number of times a user boards within a time range T.
    \item \texttt{alight\_T} Number of times a user alights within a time range T.
    \item \texttt{start\_T} User trips starting within a time range T.
    \item \texttt{end\_T} User trips ending within a time range T.
    \item \texttt{load\_X$_{LT}$} The average number of passengers traveling from the stop X to its next stop in the line L within the time range T. Can also be seen as the average load of a transport vehicle.

@@

@@

\subsection{Comparing \acumm and \ctr}
\label{sec:comp}
Better show this after they have been both explained...

\begin{threeparttable}
\caption{Efficiency of \acumm~and \ctr against the queries described in Section~\ref{sec:rq}}
\label{tab:queries}
\begin{tabular}{|l|l|l|}
\hline
Query &  \acumm & \ctr\\
\hline
\texttt{board\_X$_{LT}$} & $O(l)$\tnote{a} & \ctrq\tnote{b} \\
\texttt{alight\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\texttt{start\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{end\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{switch\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{board\_L$_T$} & O(1) & $O(ns \times \ctrq)$\tnote{be} \\
\texttt{alight\_L$_T$} & O(1) & $O(ns \times \ctrq)$\tnote{bce} \\
\texttt{start\_L$_T$} & - & \ctrq\tnote{b} \\
\texttt{end\_L$_T$} & - & $O(ns \times log(|L|\times\bar{|J^l|}))$\tnote{ef} \\
\texttt{board\_T} & $O(l)$\tnote{a} & Hard\tnote{d} \\
\texttt{alight\_T} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\texttt{start\_T} & - & $O(|L| \times log\bar{|J^l|})$\tnote{f} \\
\texttt{end\_T} & - & Hard\tnote{d} \\
\texttt{load\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\hline
\end{tabular}

\begin{tablenotes}
\item[a] $l$ is the number of lines we restrict to.
\item[b] The complexity of a \ctrq~query varies with the restrictions.
\item[c] May include false positives.
\item[d] Not practical to solve with the indexing capabilities of \ctr.
\item[e] $ns$ is the number of stops in the line L.
\item[f] $|L|$ is the total number of lines represented, and $\bar{|J^l|}$ is the average number of jcodes per line.
\end{tablenotes}
\end{threeparttable}

In \ctr, the only alighting stops that are explicitly represented are the final stops. To obtain an approximated count of the rest of them, we would need to extract and examine all the occurrences for board\_W$_{LT}$ for every W that could have been boarded before X, as the worst-case time complexity of solving with the index operations is prohibitive.
